Adaptive Scheduling of Scientific Workflows\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-06 main.tex
Added Results:memory usage

    On the normal cluster and among small workflows, the makespans produced by \heftbl and \heftblc are $1$\% worse than the baseline,
    \heftmm $19$\% worse.
    For middle-sized ones \heftmm is $12.3$\% worse, the rest is also $1-2$\% worse.
    For the big workflows however, the results of \heftbl and \heftblc are $<1$\% worse and \heftmm is only $9$\% worse.
    The heuristics pay off more on larger workflows.
    \subsubsection{Memory usage}
    \subsubsection{Impact of cluster size}
    On a cluster with only 6 processors (1 of each kind), the baseline makes more failures: from $43.4$\%  (small workflows)
    to $88.9$\% (mid-sized) and $94.4$\% (big workflows).
    These values also become more unattainable: the makespans heuristics produce are worse by $3-12$\% (\heftbl) to $12-52$\%
    (\heftmm).
    However, these comparisons are less expressive, because most of baseline solutions are invalid.
    \skug{TODO: add numbers about failures on the small cluster with the fixed bug}

>>>>

    On the normal cluster and among small workflows, the makespans produced by \heftbl and \heftblc are $1$\% worse than the baseline,
    \heftmm $19$\% worse.
    For middle-sized ones \heftmm is $12.3$\% worse, the rest is also $1-2$\% worse.
    For the big workflows however, the results of \heftbl and \heftblc are $<1$\% worse and \heftmm is only $9$\% worse.
    The heuristics pay off more on larger workflows.
    \subsubsection{Memory usage}
    Minimizing memory usage is an interesting measure of the quality of the solution produced by a heuristic.
    We studied the average peak memory consumption in our cluster.
    We looked at the maximum memory usage on each processor during a task execution, and averaged it over all processors
    in the execution environment.

    The results adhere to the intuition: \heftmm produces consistently smaller memory usage among all the heuristics.
    So, for small workflows, the average memory occupation by \heftbl and \heftblc is $11.8$\% and $11.7$\%, respectively,
    while \heftmm manged to occupy $10.2$\% of memories.
    For middle-sized workflows, \heftbl and \heftblc occupied $27.8$\% and $28.2$\%, respectively, while \heftmm occupied
    $21$\%.
    For the big workflows, \heftmm occupied $20.9$\% against $33.7$\% by \heftbl and $27.6$\% by \heftblc.
    Interestingly, for big workflows, \heftmm occupied on average even a little less that for the middle-sized ones.
    This means that the bound of exploiting parallelization has been achieved for workflows around the size of middle-sized ones,
    and for the big workflows, the makespan is not improved by ``spreading'' the workflow more.

    \subsubsection{Impact of cluster size}
    On a cluster with only 6 processors (1 of each kind), the baseline makes more failures: from $43.4$\%  (small workflows)
    to $88.9$\% (mid-sized) and $94.4$\% (big workflows).
    These values also become more unattainable: the makespans heuristics produce are worse by $3-12$\% (\heftbl) to $12-52$\%
    (\heftmm).
    However, these comparisons are less expressive, because most of baseline solutions are invalid.
    \skug{TODO: add numbers about failures on the small cluster with the fixed bug}
